%% ---------------------------------------------------------------------------%
%% main.tex - Part 3 Project Final Report, Ricardo da Silva
%% SEE http://latex.knobs-dials.com
%% tab_size: 2
%% ---------------------------------------------------------------------------%
% Preamble
\documentclass{ecsproject}     			% Use the ECS Project Style
\usepackage[square,numbers]{natbib}	% Use Natbib style for the refs.
\graphicspath{{../Figures-Final/}}  % Location of figures
\hypersetup{colorlinks=true}				% Set to false for b/w printing
\setboolean{@twoside}{true}				% Set true for a page gutter

\usepackage[disable]{todonotes}  		% Possible option: disable
\newcommand{\inote}[1]{\todo[inline]{#1}}  % type \inote{bla bla}

\usepackage[titletoc]{appendix}     % Put 'Appendix' in TOC
\usepackage{array}

%\input{Definitions}                % Include abbreviations
\usepackage[intoc]{nomencl}					% Use the nomenclature package
\makenomenclature % TODO: run `makeindex Main.nlo -s nomencl.ist -o Main.nls`
\renewcommand{\nomname}{Nomenclature and Abbreviations}

\newcommand{\meq}[2] {							% Equation macro. \meq{label}{math}
	\begin{align} \label{eq:#1} #2
	\end{align}
}

\newcommand{\about}{\raise.17ex\hbox{$\scriptstyle\sim$}}

\newcommand{\dobib}[1] {
  \if@openright
    \cleardoublepage
  \else
    \clearpage
  \fi
  \addtotoc{\bibname}
  \bibliography{#1}
}

\lstdefinestyle{customc}{						% Custom C listing style
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  frame=L,
  xleftmargin=\parindent,
  language=C,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries\color{green!40!black},    % Comment out for b/w
  commentstyle=\itshape\color{purple!40!black},
  identifierstyle=\color{blue},
  stringstyle=\color{orange},
}

\def\figwidth{0.8\textwidth}    % Figure width used for most figures

\renewcommand{\arraystretch}{1.3}  % Increase row separation in tables

%\includeonly{,,} % Only compile these files
%% ---------------------------------------------------------------------------%
\begin{document}
\frontmatter
\title      {Speech Recognition on Embedded Hardware}
\authors    {\texorpdfstring
             {\href{mailto:rmds1g10@ecs.soton.ac.uk}{Ricardo da Silva}}
             {Ricardo da Silva}
            }
\addresses  {\groupname\\\deptname\\\univname}
\date       {April, 2013} % {\today}
\subject    {}
\keywords   {}
\supervisor {Professor Steve Gunn}
\examiner   {Dr Nick Harris}
\degree     {Electronic Engineering with Mobile and Secure Systems} %TODO fix
\maketitle
\begin{abstract}  % 141 words
% the Abstract summarises the purpose of the project and what was achieved by the project.
This report presents a proof of concept system that is aimed at investigating Hidden Markov Model based speech recognition in embedded hardware.  It makes use of two new electronic boards, based on a Spartan 3 FPGA and an ARMv5 Linux applications processor, that are currently under development at the University of Southampton.  Speech data is pre-processed in Linux, by performing spectral analysis followed by a Discrete Cosine transformed filterbank analysis, to produce Mel Frequency Cepstral Coefficients.  Given this observation data, the FPGA performs the most computationally intensive part of a modern HMM based speech recognition system -- evaluating the state emission probabilities.  It is shown that the FPGA is capable of performing these calculations faster than a software implementation on the Linux processor.  The resulting system is also a valuable example of how these two boards may be used in a practical setting.
\end{abstract}
\tableofcontents
\listoffigures
%\listoftables
%\lstlistoflistings
%\listofsymbols{ll}{$w$ & The weight vector}
\clearpage
\markboth{\nomname}{\nomname}
\printnomenclature
\cleardoublepage
\acknowledgements{
My biggest thanks go to Professor Steve Gunn, for being such a great and supporting supervisor.  Thank you also for letting me contribute to the Micro Arcana development.

Thanks to Srinandan Dasmahapatra for his time and the advice he gave me on Hidden Markov Models and Speech Recognition.

Finally, thanks to my parents and friends for always being there when I needed it.
}
\authorshipdeclaration{Ricardo da Silva}
%\dedicatory{To \dots}
%% ---------------------------------------------------------------------------%
% See https://cs.uwaterloo.ca/~brecht/thesis-hints.html
\mainmatter

\include{Introduction}    % Mostly done
\include{Background}      % Partially.  Needs expansion on FPGA stuff
\include{Approach}        % Needs tidying up
\include{Implementation}  % 
\include{Testing}         % Mostly done, needs expansion
\include{Analysis}        % 
\include{Conclusions}     % Mostly done

%% ---------------------------------------------------------------------------%
\bibliographystyle{plainnat}  % TODO: fix ecs bib style...
\dobib{../citations-ALL}

\appendices
\input{Appendices/Index}
%% ---------------------------------------------------------------------------%
\end{document}
