%!TEX root = ../Main.tex
% Archive Tree
\chapter{File Archive Contents} % (fold)
\label{apdx:archive_contents}

Below is a full tree and description of the files included in the archive submitted along with this report.

% Source files
% 	SystemVerilog code
% 	Testbenches
% 	Lisp utilities
% 	Compiled versions of code

% Files for dev env
% 	La Papessa constraints
% 	Spec file for FFTW



\texttt{Source/GDP-in-C} \\
- A C program which calculates senone scores; built to get an idea of the time a conventional processor takes to perform the calculations.

\texttt{Source/GPIO-test} \\
- A program to help measure the switching speed of memory mapped GPIO.

\texttt{Source/Utilities} \\
- The Common Lisp software utilities.  The HMM definitions used for the project are also in this folder.

\texttt{Source/C-backend} \\
- This is the main pre-processor application code.  A Makefile is included to facilitate building the code, which should then run on L'Imperatrice.  A sample WAV file is also included.

\texttt{Source/SystemVerilog-Main} \\
- This is the main SystemVerilog code that was built for the project.

\texttt{Source/SystemVerilog-Simulation} \\
- These are the testbenches and models required to test the modules provided in SystemVerilog-Main


\texttt{Binaries/} \\
- This folder contains a set of pre-compiled binary files and SVF files which may be transferred to L'Imperatrice or La Papessa without modification.  This includes binaries for all the programs stored in the Source directory.  There are two SVF files -- one writes the program to flash on the FPGA; the other is only a temporary (fast) write.


\texttt{DevEnv/} \\
- This folder contains various files that were important in the development environment.


\texttt{Screenshots} \\
- This folder includes other screenshots taken during the design and simulation stage of the project, that were not given in the main report body.


Below is a tree of the files included in the archive.

\begin{lstlisting}
Archive
├── Binaries
│   ├── fftw-test
│   ├── gdp-test
│   ├── gpio-test
│   ├── pre-process
│   ├── top-level-12s6.svf
│   └── top-level-12s6c-flash.svf
├── DevEnv
│   ├── La Papessa Contraints.txt
│   └── fftw.spec
├── Screenshots
│   ├── DesignHeirarchy.PNG
│   ├── GDP controller test 10 senones.PNG
│   ├── Logic
│   │   ├── view addr.png
│   │   └── view ce etc.png
│   ├── Send module closeup with sram model.PNG
│   ├── Send module full test with sram model.PNG
│   ├── Send module run twice.PNG
│   ├── Top level - PROC to NORM.PNG
│   ├── Top level - PROC to end of SEND.PNG
│   ├── Top level - PROC to start of SEND.PNG
│   ├── Top level - virtual memory being changed.PNG
│   ├── Top level FULL Cycle.PNG
│   └── UART receiving data.PNG
└── Source
    ├── C-backend
    │   ├── Makefile
    │   ├── gpio.c
    │   ├── gpio.h
    │   ├── libmfcc
    │   │   ├── libmfcc.c
    │   │   └── libmfcc.h
    │   ├── main.c
    │   ├── main.h
    │   ├── obj
    │   │   └── libmfcc
    │   ├── preProcess.c
    │   ├── preProcess.h
    │   ├── sample.c
    │   ├── sample.h
    │   ├── sample1.wav
    │   ├── serial.c
    │   └── serial.h
    ├── FFTW
    │   ├── fftw_test.c
    │   ├── libmfcc.c
    │   └── libmfcc.h
    ├── GDP-in-C
    │   └── gdp-test.c
    ├── GPIO-test
    │   ├── gpio.c
    │   ├── gpio.h
    │   └── main.c
    ├── SystemVerilog-Main
    │   ├── all_s_data.sv
    │   ├── gdp.sv
    │   ├── gdp_controller.sv
    │   ├── max.sv
    │   ├── normaliser.sv
    │   ├── send.sv
    │   ├── sram.sv
    │   ├── top_level.sv
    │   ├── uart
    │   │   ├── baudgen.sv
    │   │   ├── uart_rx.sv
    │   │   └── uart_tx.sv
    │   └── uart.sv
    ├── SystemVerilog-Simulation
    │   ├── sram_model.sv
    │   ├── test_baudgen.sv
    │   ├── test_gdp.sv
    │   ├── test_gdp_controller.sv
    │   ├── test_send.sv
    │   ├── test_top_level.sv
    │   └── test_uart.sv
    └── Utilities
        ├── extract.lisp
        ├── hmmdefs
        └── main.lisp

16 directories, 64 files
\end{lstlisting}
