%!TEX root = ../Main.tex
% Development Environement
\chapter{Development Environment} % (fold)
\label{apdx:development_environment}


\section{FPGA design cycle} % (fold)
\label{apdx:fpga_design_cycle}
	As mentioned in the report, Synplify Premier was used to synthesise the SystemVerilog code.  Then, the ISE Webpack (including the Floorplanner software) was used to assign ports to physical pins, and generate programming files.  Finally, urJTAG was used to actually program the device over JTAG.

	In order to use Xilinx design tools with Synplify, the correct environment variable must be set.  Under the Options menu, select `P\&R Environment Options'.  The XILINX variable must be set to the path of the Xilinx ISE tools (e.g., C:\textbackslash Xilinx\textbackslash 14.1\textbackslash ISE\_DS\textbackslash ISE).  From the same menu, go to the Xilinx Submenu, and now `Start ISE Project Navigator' should work correctly.

	In addition, the implementation options for Synplify must be correctly set -- in particular the correct part must be selected, and appropriate timing constraints entered.  The onboard 50MHz clock needs one such constraint.

	Once this is set up, the design process roughly follows this sequence:
	\begin{enumerate}
		\item Write SystemVerilog code in Synplify.
		\item Run Synplify implementation; fix errors until it synthesises correctly.
		\item Open project with Xilinx design tools (via Options menu).
		\item Either manually edit the constraints file and add net to port mappings, or use the Floorplanner (post-synthesis) tool to do this.
		\item Run the ISE Webpack implementation.  If mapping fails, the design may be too big to fit on the device.
		\item Generate .bit programming file.
		\item Open the `iMPACT' software (which comes with the ISE Webpack).
		\item Create a new project, and select the .bit file created in the previous step.
		\item From the Output menu, select create new SVF file.
		\item Perform whichever actions required from the list on the left -- programming the flash takes a long time, so if still in the testing stages, only run `Program FPGA'.
		\item End the SVF output (from the same menu as before).  This step is very important!
		\item Open urJTAG and connect to the programming cable.
		\item Use `svf programming-file.svf' to transfer the design to La Papessa!
	\end{enumerate}

	As this process is fairly long, it may be useful to speed some parts up.  In particular, instead of repeatedly assigning pins with Floorplanner, it's easier to copy the constraints file once everything is assigned correctly.  Then when Webpack is opened again, and the constraints are automatically overwritten, simply copy in the correct pin assignments.  The constraints used for this project are available in the file archive, in the DevEnv folder.
% sectapdx fpga_design_cycle (end)



\section{LTIB usage} % (fold)
\label{apdx:ltib_usage}

	\subsection{Cross compiling} % (fold)
	\label{apdx:cross_compiling}
		To compile code that will work on L'Imperatrice, the binaries installed by LTIB must be used.  They are normally stored in:

		\texttt{/opt/freescale/usr/local/gcc-x-glibc-x-x/arm-none-gnueabi/\\*
		arm-none-linux-gnueabi/bin/}
		  
		Running the following command will add this to the path (\$ is the prompt):

		\texttt{\$ PATH=/opt/freescale/usr/local/gcc-4.1.2-glibc-2.5-nptl-3/\\*
		arm-none-linux-gnueabi/arm-none-linux-gnueabi/bin/:\$PATH}

		Then running `gcc' will automatically use the arm version.
	% subsectapdx cross_compiling (end)


	\subsection{GPIO and UART} % (fold)
	\label{apdx:gpio_and_uart}
		Both GPIO and UART are optional components that must be enabled in the LTIB configuration.  
			%TODO!!!
	% subsectapdx gpio_and_uart (end)


	\subsection{Compiling FFTW for LTIB} % (fold)
	\label{apdx:compiling_fftw_for_ltib}
		%Read: http://ltib.org/documentation-LtibFaq
		In many cases one may want to build a library or package to install on L'Imperatrice.  For example, one may want to perform real time Fast Fourier Transforms using the FFTW library, which has native support for ARMv5 devices.  The general procedure, as described in the FAQ at \href{http://ltib.org/documentation-LtibFaq}{http://ltib.org/documentation-LtibFaq}, is:
		\begin{enumerate}
			\item Prepare the source files
			\item Build and install the package to the rootfs using LTIB
			\item Add -I and -L flags to gcc to cross compile with the libraries that were just installed.
		\end{enumerate}

		The FFTW source can be downloaded from \href{http://www.fftw.org/download.html}{http://www.fftw.org/download.html}.  In order to add it to LTIB, a custom RPM spec file was created, available in the project file archive in the DevEnv folder.  Then the ltib binary is used to correctly configure and build FFTW from source, and add it to the list of installed packages.  This allows FFTW to be selected in the `Packages list' in the LTIB configuration menu, and thus installed in the rootfs.

		When compiling a C program that uses FFTW, the relevant library and include paths must be added.  In this project, a Makefile was used to automate the build process.
	% subsection compiling_fftw_for_ltib (end)
% section ltib_usage (end)


\section{Notes on L'Imperatrice} % (fold)
\label{apdx:notes_on_l_imperatrice}
	In order to connect the two boards via ribbon cable, a couple of extra features had to be implemented.

	The Application UART on L'Imperatrice is on Port 2, which is also where the Debug UART lives.  In order to still be able to connect to the debug UART once the two boards were connected, the signals were rerouted inside the FPGA, so that Debug UART appeared on a different port on La Papessa.

	When L'Imperatrice boots, one of its pins (LRADC0) must be held high (or floating), or it will select the wrong boot sequence (and fail with a Kernel panic).  However, if La Papessa is connected to the board after boot, the sudden load on the voltage regulator causes the chip to reboot, and then fail due to LRADC0 being pulled low by the FPGA.  In order to fix this, an output on the FPGA is assigned to be permanently high, and then routed to this pin.
% sectapdx notes_on_l_imperatrice (end)

% chapter development_environment (end)