%!TEX root = ../Main.tex
% Voxforge
\chapter{Voxforge} % (fold)
\label{apdx:voxforge}


\section{Audacity Recording} % (fold)
\label{apdx:audacity_recording}
	The settings used to record the speech samples using Audacity are shown below.
	\begin{itemize}
		\item Sampling rate: 48KHz
		\item Output format: Uncompressed Microsoft WAV, 16bit unsigned
		\item Output channels: 1 (mono)
	\end{itemize}
% section audacity_recording (end)


\section{Model Adaptation} % (fold)
\label{apdx:model_adaptation}
	A set of speech models were downloaded from the Voxforge website, which were analysed and used throughout the project.  However, they were first adjusted to the author's voice, in order to gain familiarity with various tools and technologies involved.

	A script to perform the adaptation was created, according to the Voxforge adaptation tutorial.  The required operations are listed here.  This script uses the `downsample.pl' script which is available for download on the Voxforge tutorial website.  It essentially runs each of the files through the sox utility.

	Note: v3.2 HTK binaries should be used.  Newer ones introduce a feature which makes these commands un-usable.

\lstset{ %
	breaklines=true,
	numbers=left,
	language=bash,
	commentstyle=\color{gray}
}

\begin{lstlisting}[]
# Path to HTK binaries
HTK=~/Documents/University/Part3/Part-3-Project/HTK/htk-bin-3.2.1

# Downsample the recorded audio to 8kHz -> wav/sample{1-31}.wav
./downsample.pl FilesToBeDownsampled wav 48000 8000

# Create the mfccs from the downsampled audio -> mfccs/sample{1-31}.mfc
$HTK/HCopy -A -D -T 1 -C wav_config -S codetrain.scp

# Re-Align the data
# Watch for errors in this!!! -> adaptPhones.mlf
$HTK/HVite -A -D -T 1 -l '*' -o SWT -b SENT-END -C config -H macros -H hmmdefs -i adaptPhones.mlf -m -t 250.0 150.0 1000.0 -y lab -a -I adaptWords.mlf -S adapt.scp dict tiedlist

# Build regression class tree -> hmm16/{hmmdefs,macros}
$HTK/HHEd -H macros -H hmmdefs -M hmm16 regtree.hed tiedlist

# Static adaptation time!
# 1. Global adaptation -> global.tmf
$HTK/HEAdapt -C config -g -S adapt.scp -I adaptPhones.mlf -H hmm16/macros -H hmm16/hmmdefs -K global.tmf -t 250.0 150.0 3000.0 tiedlist

# 2. Transform models -> hmmAdapt/{hmmdefs,macros}
$HTK/HEAdapt -C config -S adapt.scp -I adaptPhones.mlf -H hmm16/macros -H hmm16/hmmdefs -J global.tmf -M hmmAdapt -t 250.0 150.0 3000.0  -j 0.9 -i 10 tiedlist
\end{lstlisting}

% section model_adaptation (end)


% chapter voxforge (end)